---
title: "Hands in motion - PAL study"
author: "SLC, CRD, MWJ"
date: "20/07/2022"
output:
  rmdformats::downcute:
    code_folding: show
    self_contained: true
    thumbnails: false
    lightbox: true
    number_sections: true
    fontfamily: mathpazo
    geometry: top=1cm, right=1cm,bottom=1cm,left=1cm
    spacing: double
    df_print: kable
    classoption: landscape
pkgdown:
  as_is: true
---

<style type="text/css">

h1.title {
  font-size: 40px;
  color: Black;
  font-weight: bold;
  text-align: center;
}
h4.author { /*  */
    font-size: 28px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  font-weight: bold;
  text-align: center;
}
h4.date { /*  */
  font-size: 28px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  font-weight: bold;
  text-align: center;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE)
```


```{r, include=FALSE}
library(tidyverse)
library(simr)
library(Hmisc)
library(jtools)
library(ggthemes)
library(kableExtra)
library(afex)
library(ggsci)
library(lme4)
library(lmerTest)
library(DT)
library(psycho)
library(gridExtra)
library(ggpubr)
library(ggstatsplot)
library(knitr)
library(effsize)
library(rmdformats)
library(outliers)
library(vtree)
library(mousetrap)
library(pastecs)
```




```{r include = FALSE}
library(readr)
library(nloptr)
library(ggplot2)


table.glmer.logit.kable <- function(x,file=""){
  coefs=coef(summary(x))
  coefs <- cbind(coefs, coefs[,1])
  coefs[,1] <- round(coefs[,1],digits=2)
  coefs[,2] <- round(coefs[,2],digits=2)
  coefs[,4] <- round(coefs[,4],digits=3)
  coefs[,5] <- round(exp(as.numeric(coefs[,5])),digits=2)
  coefs<-coefs[,-3]
  colnames(coefs) <- c("Coef (\u03b2)","SE(\u03b2)","p","OR (exp(\u03b2))")
  kable(coefs)
}

library(readr)
library(nloptr)
library(ggplot2)

table.lmer.ttop.kable <- function(x,file=""){
  require(lme4)
  require(Hmisc)
  fixedeffs=as.data.frame(fixef(x))
  temp <- as.data.frame(confint(x, method="Wald"))
  fixedeffs[c(2,3)] <- subset(temp, !is.na(temp[,2]))
  # extract coefficients
  coefs <- data.frame(coef(summary(x)))
  # use normal distribution to approximate p-value
  fixedeffs[c(4)] <- 2 * (1 - pnorm(abs(coefs$t.value)))
  fixedeffs[,1] <- round(fixedeffs[,1],digits=3)
  fixedeffs[,2] <- round(fixedeffs[,2],digits=3)
  fixedeffs[,3] <- round(fixedeffs[,3],digits=3)
  fixedeffs[,4] <- round(fixedeffs[,4],digits=3)
  fixedeffs[1,c(4)]="-"
  colnames(fixedeffs) <- c("Coef (\u03b2)","Lower (\u03b2)","Upper (\u03b2)","p")
  kable(fixedeffs)
}
```



```{r}
HandsInMotionMainTaskFiltered <- read.csv("~/HandsInMotion_Recognition_Behavioural.csv") # ~ INSERT_HOME_DIRECTORY

HandsInMotionMainFiltered <- HandsInMotionMainTaskFiltered %>% 
  mutate(id_no = ifelse(id_no == 10083, 183, id_no)) # incorrectly entered ppt number
```


```{r}
HandsInMotionPPTs <- HandsInMotionMainFiltered %>% 
  dplyr::select(id_no) %>% 
  distinct() %>% 
  arrange(id_no)
```


# **Demographic information** {.tabset .tabset-pills}


```{r}
HandsInMotionBackgroundTestsFile <- read.csv("~/HandsInMotion_BackgroundTests.csv") # ~ INSERT_HOME_DIRECTORY
```

```{r}
HandsInMotionBackgroundTests <- HandsInMotionBackgroundTestsFile %>% 
  mutate(WRATWordR_MeanScore = WordRAcc_totalScore/70,
         WordRF_meanScore_all = WordRF_totalScore_all/144,
         PseudoWordRF_meanScore_all = PseudoWordRF_totalScore_all/144,
         RANcompositeDur = RANDigitsDurTotal + RANLettersDurTotal) %>% 
  mutate(WRATWordR_totalScore_Z = scale(WordRAcc_totalScore, center = TRUE, scale = TRUE),
         WordRF_totalScore_Z = scale(WordRF_totalScore_all, center = TRUE, scale = TRUE),
         PseudoWordRF_totalScore_Z = scale(PseudoWordRF_totalScore_all, center = TRUE, scale = TRUE),
         PD_Z = scale(PD_TotalScore, center = TRUE, scale = TRUE),
         RANcompositeDur_Z = scale(RANcompositeDur, center = TRUE, scale = TRUE),
         compositeAll = WordRF_totalScore_all + PseudoWordRF_totalScore_all + WordRAcc_totalScore,
         medianAll = median(compositeAll),
         medianAllLabel = ifelse(compositeAll >= medianAll,"Typical Reader", "Poorer Reader"))
```



## **Gender**



```{r fig.align="center", out.width = '100%', out.extra='style="background-color: #313436; padding:6px; display: inline-block;"'}
vtree(HandsInMotionBackgroundTests, "Gender",
      horiz= FALSE,
      plain = TRUE,
      labelvar = c(Gender = "Gender"))
```


## **Age** {.tabset .tabset-pills}


### **Descriptive Statistics** {.tabset .tabset-pills}


#### **Overall**


```{r}
psych::describe(HandsInMotionBackgroundTests$age)
```



# {-}



# **PAL recognition Task** {.tabset .tabset-pills}


```{r}
HandsInMotionFS <- read.csv("~/HandsInMotion_FactorScore.csv") # ~ INSERT_HOME_DIRECTORY
```


```{r}
HandsInMotionMainBackTests <- inner_join(HandsInMotionMainFiltered, HandsInMotionBackgroundTests, by = "id_no") %>% 
  mutate(ReadingGroup = ifelse(medianAllLabel == "Typical Reader", 0,1)) %>% 
  rename(participant_id = Participant.Private.ID) %>% 
  inner_join(., HandsInMotionFS, by = "id_no")
```



## **Accuracy** {.tabset .tabset-pills}



```{r}
HandsInMotionMainGeneralSummaryPPT <- HandsInMotionMainBackTests %>% 
  group_by(Age_Months, id_no, medianAllLabel,compositeAll, ReadingGroup) %>% 
  summarise(TwoChoiceTotal = sum(Accuracy),
            TwoChoiceMean = TwoChoiceTotal/36,
            TwoChoiceMeanRT = mean(RT))
```

```{r}
psych::describe(HandsInMotionMainGeneralSummaryPPT$TwoChoiceTotal)
```


```{r}
psych::describe(HandsInMotionMainGeneralSummaryPPT$TwoChoiceMean)
```



### **Recognition Accuracy Linear Models** {.tabset .tabset-pills}

```{r}
HandsInMotion_lm_df <- HandsInMotionMainBackTests 

HandsInMotion_lm_df$id_no <- as.factor(HandsInMotion_lm_df$id_no) 
HandsInMotion_lm_df$target_shape <- as.factor(HandsInMotion_lm_df$target_shape)

HandsInMotion_lm_df$cAge_Months <- scale(HandsInMotion_lm_df$Age_Months, center = TRUE, scale = FALSE)
```


#### **Model 1: Latent variable (WRAT + WRF + PWRF)**

```{r}
HandsInMotionModelAcc1 <- glmer(Accuracy ~ 1 + read_fs +
                             (1 | target_shape) +
                             (1 | id_no), 
                           data = HandsInMotion_lm_df, 
                           family = binomial,
                           control=glmerControl(optimizer="nloptwrap",
                                                calc.derivs = FALSE, 
                                                optCtrl=list(maxfun=40000)))
```

```{r}
summary(HandsInMotionModelAcc1)
```

```{r, results='asis'}
table.glmer.logit.kable(HandsInMotionModelAcc1)
```



- **Bootstrapped confidence intervals**

```{r, eval = TRUE}
confint.merMod(HandsInMotionModelAcc1, parm = "beta_", method = "boot", nsim=1000)
```



#### **Model 2: Latent variable (WRAT + WRF + PWRF + Age as a covariate)**

```{r}
HandsInMotionModelAcc2 <- glmer(Accuracy ~ 1 + cAge_Months + read_fs +
                             (1 | target_shape)+
                             (1 | id_no), 
                           data = HandsInMotion_lm_df, 
                           family = binomial,
                           control=glmerControl(optimizer="nloptwrap",
                                                calc.derivs = FALSE, 
                                                optCtrl=list(maxfun=40000)))
```

```{r}
summary(HandsInMotionModelAcc2)
```

```{r, results='asis'}
table.glmer.logit.kable(HandsInMotionModelAcc2)
```






## **Reaction Time** {.tabset .tabset-pills}


```{r}
HandsInMotionMainBackTests_RT <- HandsInMotionMainBackTests %>% 
  filter(Accuracy == 1)
```

```{r}
psych::describe(HandsInMotionMainBackTests_RT$RT)
```




### **Recognition Reaction Time Linear Models** {.tabset .tabset-pills}


```{r}
HandsInMotion_lm_RT_df <- HandsInMotionMainBackTests_RT

HandsInMotion_lm_RT_df$id_no <- as.factor(HandsInMotion_lm_RT_df$id_no) 
HandsInMotion_lm_RT_df$target_shape <- as.factor(HandsInMotion_lm_RT_df$target_shape)

HandsInMotion_lm_RT_df$logRT <- log(HandsInMotion_lm_RT_df$RT)

HandsInMotion_lm_RT_df$cAge_Months <- scale(HandsInMotion_lm_RT_df$Age_Months, center = TRUE, scale = FALSE)
```


#### **Model 1: Latent variable (WRAT + WRF + PWRF)**



```{r}
HandsInMotionModelRT1 <- lmer(logRT ~ 1 + read_fs +
                             (1 | target_shape)+
                             (1 | id_no), 
                           data = HandsInMotion_lm_RT_df, 
                           control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE, optCtrl = list(maxfun = 20000)))
```

```{r}
summary(HandsInMotionModelRT1)
```


```{r results='asis'}
table.lmer.ttop.kable(HandsInMotionModelRT1)
```



#- **Bootstrapped confidence intervals**

```{r, eval = TRUE}
confint.merMod(HandsInMotionModelRT1, parm = "beta_", method = "boot", nsim=1000)
```






#### **Model 2: Latent variable (WRAT + WRF + PWRF + Age as a covariate)**



```{r}
HandsInMotionModelRT2 <- lmer(logRT ~ 1 + cAge_Months + read_fs +
                             (1 | target_shape)+
                             (1 | id_no), 
                           data = HandsInMotion_lm_RT_df, 
                           control = lmerControl(optimizer = "nloptwrap", calc.derivs = FALSE, optCtrl = list(maxfun = 20000)))
```

```{r}
summary(HandsInMotionModelRT2)
```


```{r results='asis'}
table.lmer.ttop.kable(HandsInMotionModelRT2)
```




# {-}




# **Mousetracking Data** {.tabset .tabset-pills}


## **Filtering steps** {.tabset .tabset-pills}


```{r}
HandsInMotionMousetrackingFile <- read.csv("~/HandsInMotion_Mousetracking.csv") # ~ INSERT_HOME_DIRECTORY
```



```{r}
id_Nos <- HandsInMotionMainBackTests %>% 
  dplyr::select(participant_id, id_no,Age_Months, medianAllLabel) %>% 
  distinct()
```


```{r}
HandsInMotionMousetrackingFile_idNo <- inner_join(HandsInMotionMousetrackingFile, id_Nos, by = "participant_id")
```


```{r}
HandsInMotionMousetrackingFile_idNo_filtered <- HandsInMotionMousetrackingFile_idNo %>% 
  dplyr::filter(type == "mouse", screen_index == 10) %>% 
  dplyr::select(id_no, participant_id,Age_Months,time_stamp, spreadsheet_row,x_normalised,y_normalised,medianAllLabel) %>% 
  group_by(id_no,participant_id, spreadsheet_row) %>% 
  mutate(ReadingGroup = medianAllLabel)

HandsInMotionMousetrackingFile_idNo_filtered$x_normalised <- as.numeric(HandsInMotionMousetrackingFile_idNo_filtered$x_normalised)
HandsInMotionMousetrackingFile_idNo_filtered$y_normalised <- as.numeric(HandsInMotionMousetrackingFile_idNo_filtered$y_normalised)
```



```{r}
behavioural_data_filtered <- HandsInMotionMainBackTests %>% 
  dplyr::select(id_no:target_shape) %>% 
  rename(spreadsheet_row = Spreadsheet.Row) %>% 
  dplyr::select(-RT) %>% 
  filter(Accuracy == 1) %>% 
  dplyr::select(id_no,spreadsheet_row,Accuracy,target_shape)
```



```{r}
HandsInMotionMousetrackingBehavioural <- inner_join(behavioural_data_filtered,HandsInMotionMousetrackingFile_idNo_filtered, by = c("id_no", "spreadsheet_row")) %>% 
  inner_join(., HandsInMotionFS, by = "id_no")
```


```{r}
gorilla.traj <- HandsInMotionMousetrackingBehavioural
```




```{r, warning = FALSE}
HandsInMotion.mt<-mt_import_long(gorilla.traj, xpos_label="x_normalised", ypos_label="y_normalised", timestamps_label="time_stamp",
                           mt_id_label= c("id_no", "spreadsheet_row"))
```



```{r}
HandsInMotion.mt<-mt_measures(HandsInMotion.mt, use = "trajectories",save_as="measures",
                        dimensions = c("xpos", "ypos"), timestamps = "timestamps",
                        verbose = FALSE)

```





```{r}
HandsInMotion.mt <-mt_count(HandsInMotion.mt, save_as = "data")
```



```{r}
HandsInMotion.mt$data$pos_var <- apply(HandsInMotion.mt$trajectories[,,"xpos"],1,var,na.rm=TRUE) + apply(HandsInMotion.mt$trajectories[,,"ypos"],1,var,na.rm=TRUE)
```



```{r}
table(HandsInMotion.mt$data$pos_var==0)
```


```{r}
HandsInMotion.mt <- mt_subset(HandsInMotion.mt, pos_var>0)
```



```{r}
nrow(HandsInMotion.mt$data)
nrow(HandsInMotion.mt$measures)
```



```{r}
HandsInMotion.mt <- mt_derivatives(HandsInMotion.mt)
```



```{r}
HandsInMotion.mt <- mt_align_start(HandsInMotion.mt)
```


```{r}
HandsInMotion.mt <- mt_remap_symmetric(HandsInMotion.mt)
```



```{r}
HandsInMotion.mt <- mt_measures(HandsInMotion.mt)
```



```{r, warning = FALSE}
HandsInMotion.mt <- mt_time_normalize(HandsInMotion.mt)
```



```{r}
HandsInMotion.mt <- mt_measures(HandsInMotion.mt,use="tn_trajectories",save_as="tn_measures")
```



```{r, eval = TRUE}
mt_aggregate(HandsInMotion.mt, use="measures",use_variables=c("MAD", "AD", "AUC"), use2_variables="medianAllLabel", subject_id="id_no")
```


## **Mouse trajectories plot** {.tabset .tabset-pills}

```{r fig.align="center", out.width = '100%', out.extra='style="background-color: #313436; padding:6px; display: inline-block;"'}
mt_plot_aggregate(HandsInMotion.mt, use="tn_trajectories", x="xpos", y="ypos", linetype="ReadingGroup",subject_id="id_no", points = FALSE, size =1.1) +   
  xlab("X Position")+
  ylab("Y Position")+
  theme_classic()+
  theme(legend.title=element_blank(), 
        legend.justification=c(0,.5), 
        legend.position=c(0.07,.18),
        legend.text = element_text(size = 10),
        axis.line = element_line(colour = 'black', size = .8),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12, face = "bold"),
        legend.key.size = unit(3,"line"),
        axis.title.x=element_text(angle=0, size=12, vjust=-.5),
        axis.title.y=element_text(size=12),
        strip.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        strip.background = element_rect(colour = "black", size = 1.2),
        plot.title = element_text(lineheight=1, face="bold", size =12),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.x = element_line(colour = "black", size = 1),
        axis.ticks.y = element_line(colour = "black", size = 1))
```



```{r}
results <-merge(HandsInMotion.mt$data, HandsInMotion.mt$measures, by="mt_id")
```




```{r}
results$id_no <- as.factor(results$id_no)

results$target_shape<- as.factor(results$target_shape)

results$cAge_Months <- scale(results$Age_Months, center = TRUE, scale = FALSE)
```



## **Mousetracking measures Linear Models** {.tabset .tabset-pills}


###  **MAD** {.tabset .tabset-pills}


#### **Model 1: Latent variable (WRAT + WRF + PWRF)** {.tabset .tabset-pills}


```{r}
MAD_model <- lmer(MAD ~ 1 + read_fs +
                     (1| id_no)+
                     (1|target_shape),
                   data =results, control = lmerControl(calc.derivs = FALSE))
```

```{r}
summary(MAD_model)
```



```{r results='asis'}
table.lmer.ttop.kable(MAD_model)
```


- **Bootstrapped confidence intervals**


```{r, eval = TRUE}
confint.merMod(MAD_model, parm = "beta_", method = "boot", nsim=1000)
```






#### **Model 2: Latent variable (WRF + PWRF + WRAT + Age as a covariate)** {.tabset .tabset-pills}

```{r}
MAD_model2 <- lmer(MAD ~ 1 + cAge_Months + read_fs +
                     (1| id_no)+
                     (1|target_shape),
                   data =results, control = lmerControl(calc.derivs = FALSE))
```

```{r}
summary(MAD_model2)
```



```{r results='asis'}
table.lmer.ttop.kable(MAD_model2)
```




### **AD** {.tabset .tabset-pills}



#### **Model 1: Latent variable (WRAT + WRF + PWRF)** {.tabset .tabset-pills}


```{r}
AD_model <- lmer(AD ~ 1 + read_fs +
                     (1| id_no)+
                   (1|target_shape),
                   data =results, control = lmerControl(calc.derivs = FALSE))
```


```{r}
summary(AD_model)
```



```{r results='asis'}
table.lmer.ttop.kable(AD_model)
```




- **Bootstrapped confidence intervals**


```{r, eval = TRUE}
confint.merMod(AD_model, parm = "beta_", method = "boot", nsim=1000)
```





#### **Model 2: Latent variable (WRAT + WRF + PWRF + Age as a covariate)** {.tabset .tabset-pills}


```{r}
AD_model2 <- lmer(AD ~ 1 + cAge_Months + read_fs +
                     (1| id_no)+
                   (1|target_shape),
                   data =results, control = lmerControl(calc.derivs = FALSE))
```


```{r}
summary(AD_model2)
```



```{r results='asis'}
table.lmer.ttop.kable(AD_model2)
```




### **AUC** {.tabset .tabset-pills}


#### **Model 1: Latent variable (WRAT + WRF + PWRF)** {.tabset .tabset-pills}

```{r}
AUC_model <- lmer(AUC ~ 1 + read_fs +
                     (1| id_no)+
                   (1|target_shape),
                   data =results, control = lmerControl(calc.derivs = FALSE))
```



```{r}
summary(AUC_model)
```



```{r results='asis'}
table.lmer.ttop.kable(AUC_model)
```



- **Bootstrapped confidence intervals**


```{r, eval = TRUE}
confint.merMod(AUC_model, parm = "beta_", method = "boot", nsim=1000)
```



#### **Model 2: Latent variable (WRAT + WRF + PWRF + Age as a covariate)** {.tabset .tabset-pills}

```{r}
AUC_model2 <- lmer(AUC ~ 1 + cAge_Months + read_fs +
                     (1| id_no)+
                   (1|target_shape),
                   data =results, control = lmerControl(calc.derivs = FALSE))
```


```{r}
summary(AUC_model2)
```



```{r results='asis'}
table.lmer.ttop.kable(AUC_model2)
```



# {-}



# **PAL Interspersed recall trials** {.tabset .tabset-pills}

```{r}
interspersedFile <- read.csv("~/HandsInMotion_InterpersedCuedRecall.csv") # ~ INSERT_HOME_DIRECTORY
```


```{r}
interspersedDF <- inner_join(interspersedFile, HandsInMotionFS, by = "id_no")
```


## **Interspersed Cued-Recall Trials - Accuracy Linear Models** {.tabset .tabset-pills}

```{r}
interspersed_lm_DF <- interspersedDF 

interspersed_lm_DF$id_no <- as.factor(interspersed_lm_DF$id_no) 
interspersed_lm_DF$target_shape <- as.factor(interspersed_lm_DF$target_shape)

interspersed_lm_DF$cAge_Months <- scale(interspersed_lm_DF$Age_Months, center = TRUE, scale = FALSE)
```



### **Model 1A: Latent variable (WRAT + WRF + PWRF)** {.tabset .tabset-pills}


```{r}
HandsInMotionInterspersedModelAcc1 <- glmer(accuracy ~ 1 + read_fs +
                             (1 | target_shape)+
                             (1 | id_no), 
                           data = interspersed_lm_DF, 
                           family = binomial,
                           control=glmerControl(optimizer="nloptwrap",
                                                calc.derivs = FALSE, 
                                                optCtrl=list(maxfun=40000)))
```

```{r}
summary(HandsInMotionInterspersedModelAcc1)
```

```{r, results='asis'}
table.glmer.logit.kable(HandsInMotionInterspersedModelAcc1)
```


- **Bootstrapped confidence intervals**


```{r, eval = TRUE}
confint.merMod(HandsInMotionInterspersedModelAcc1, parm = "beta_", method = "boot", nsim=1000)
```




### **Model 2: Latent variable (WRAT + WRF + PWRF + Age as a covariate)** {.tabset .tabset-pills}


```{r}
HandsInMotionInterspersedModelAcc2 <- glmer(accuracy ~ 1+ cAge_Months + read_fs +
                             (1 | target_shape)+
                             (1 | id_no), 
                           data = interspersed_lm_DF, 
                           family = binomial,
                           control=glmerControl(optimizer="nloptwrap",
                                                calc.derivs = FALSE, 
                                                optCtrl=list(maxfun=40000)))
```

```{r}
summary(HandsInMotionInterspersedModelAcc2)
```

```{r, results='asis'}
table.glmer.logit.kable(HandsInMotionInterspersedModelAcc2)
```





```{r}
interspersedSummary <- interspersedDF %>% 
  group_by(id_no) %>% 
  summarise(InterspersedTotalScore = sum(accuracy),
            InterspersedMeanScore = mean(accuracy))
```

```{r}
psych::describe(interspersedSummary$InterspersedTotalScore)
```



```{r}
psych::describe(interspersedSummary$InterspersedMeanScore)
```




# {-}



# **PAL Separate cued-recall trials** {.tabset .tabset-pills}


```{r}
separateRecallFile <- read.csv("~/HandsInMotion_SeparateCuedRecall.csv") # ~ INSERT_HOME_DIRECTORY
```


```{r}
separateRecallFile_idNo <- inner_join(separateRecallFile, id_Nos, by = "id_no") %>% 
  inner_join(., HandsInMotionFS, by = "id_no")
```



```{r}
separateFileFiltered <- separateRecallFile_idNo %>% 
  filter(response != "NA") %>%
  mutate(accuracy = as.numeric(accuracy)) %>% 
  mutate(item = case_when(
    Trial.Number == 1 & version == "a" ~ "bix",
    Trial.Number == 2 & version == "a" ~ "fip",
    Trial.Number == 3 & version == "a" ~ "beb",
    Trial.Number == 4 & version == "a" ~ "fum",
    Trial.Number == 5 & version == "a" ~ "gex",
    Trial.Number == 6 & version == "a" ~ "saf",
    Trial.Number == 7 & version == "a" ~ "sut",
    Trial.Number == 8 & version == "a" ~ "dep",
    Trial.Number == 9 & version == "a" ~ "gop",
    Trial.Number == 10 & version == "a" ~ "dod",
    Trial.Number == 11 & version == "a" ~ "pof",
    Trial.Number == 12 & version == "a" ~ "pag",
    Trial.Number == 1 & version == "b" ~ "sut",
    Trial.Number == 2 & version == "b" ~ "dep",
    Trial.Number == 3 & version == "b" ~ "gop",
    Trial.Number == 4 & version == "b" ~ "dod",
    Trial.Number == 5 & version == "b" ~ "pof",
    Trial.Number == 6 & version == "b" ~ "pag",
    Trial.Number == 7 & version == "b" ~ "bix",
    Trial.Number == 8 & version == "b" ~ "fip",
    Trial.Number == 9 & version == "b" ~ "beb",
    Trial.Number == 10 & version == "b" ~ "fum",
    Trial.Number == 11 & version == "b" ~ "gex",
    Trial.Number == 12 & version == "b" ~ "saf",
    Trial.Number == 1 & version == "c" ~ "dod",
    Trial.Number == 2 & version == "c" ~ "pof",
    Trial.Number == 3 & version == "c" ~ "sut",
    Trial.Number == 4 & version == "c" ~ "dep",
    Trial.Number == 5 & version == "c" ~ "pag",
    Trial.Number == 6 & version == "c" ~ "gop",
    Trial.Number == 7 & version == "c" ~ "fip",
    Trial.Number == 8 & version == "c" ~ "saf",
    Trial.Number == 9 & version == "c" ~ "gex",
    Trial.Number == 10 & version == "c" ~ "fum",
    Trial.Number == 11 & version == "c" ~ "beb",
    Trial.Number == 12 & version == "c" ~ "bix"
  ))

```



```{r}
separateRecallDF <- separateFileFiltered %>% 
  dplyr::select(id_no, item, accuracy, response, Age_Months, read_fs)
```




## **Separate Cued-Recall Task - Accuracy Linear Models** {.tabset .tabset-pills}

```{r}
separateRecall_lm_DF <- separateRecallDF 

separateRecall_lm_DF$id_no <- as.factor(separateRecall_lm_DF$id_no) 
separateRecall_lm_DF$item <- as.factor(separateRecall_lm_DF$item)

separateRecall_lm_DF$cAge_Months <- scale(separateRecall_lm_DF$Age_Months, center = TRUE, scale = FALSE)
```




### **Model 1: Latent variable (WRAT + WRF + PWRF)** {.tabset .tabset-pills}

```{r}
HandsInMotionSeparateModelAcc1 <- glmer(accuracy ~ 1 + read_fs +
                             (1 | item)+
                             (1 | id_no), 
                           data = separateRecall_lm_DF, 
                           family = binomial,
                           control=glmerControl(optimizer="nloptwrap",
                                                calc.derivs = FALSE, 
                                                optCtrl=list(maxfun=40000)))
```

```{r}
summary(HandsInMotionSeparateModelAcc1)
```

```{r, results='asis'}
table.glmer.logit.kable(HandsInMotionSeparateModelAcc1)
```




- **Bootstrapped confidence intervals**


```{r, eval = TRUE}
confint.merMod(HandsInMotionSeparateModelAcc1, parm = "beta_", method = "boot", nsim=1000)
```






### **Model 2: Latent variable (WRAT + WRF + PWRF  + Age as a covariate)** {.tabset .tabset-pills}

```{r}
HandsInMotionSeparateModelAcc2 <- glmer(accuracy ~ 1+ cAge_Months + read_fs +
                             (1 | item)+
                             (1 | id_no), 
                           data = separateRecall_lm_DF, 
                           family = binomial,
                           control=glmerControl(optimizer="nloptwrap",
                                                calc.derivs = FALSE, 
                                                optCtrl=list(maxfun=40000)))
```

```{r}
summary(HandsInMotionSeparateModelAcc2)
```

```{r, results='asis'}
table.glmer.logit.kable(HandsInMotionSeparateModelAcc2)
```






```{r}
SeparateSummary <- separateRecallDF %>% 
  group_by(id_no) %>% 
  summarise(SepRecallTotalScore = sum(accuracy),
            SepRecallMeanScore = mean(accuracy))
```

```{r}
psych::describe(SeparateSummary$SepRecallTotalScore)
```


```{r}
psych::describe(SeparateSummary$SepRecallMeanScore)
```



# {-}

```{r}
HandsInMotion3tasks <- HandsInMotionBackgroundTests %>% 
  left_join(.,HandsInMotionMainGeneralSummaryPPT) %>% 
  left_join(.,interspersedSummary, by = "id_no") %>% 
  left_join(.,SeparateSummary, by = "id_no") %>% 
  group_by(id_no) %>% 
  mutate(CompositeHandsInMotionTotal = sum(TwoChoiceTotal, InterspersedTotalScore, SepRecallTotalScore, na.rm = TRUE),
         CompositeHandsInMotionMean = CompositeHandsInMotionTotal/60) %>% 
  ungroup() %>% 
  filter(!id_no %in% c(99,139,115,3)) %>% # these ppts had no cued-recall data in the separate task
  mutate (CompositeHandsInMotionTotal_Z = scale(CompositeHandsInMotionTotal, center = TRUE, scale = TRUE)) %>% 
  left_join(., HandsInMotionFS, by = "id_no")
```



```{r}
psych::describe(HandsInMotion3tasks$CompositeHandsInMotionMean)
```


# **Accuracy across all PAL tasks**


## **Linear Model**


```{r}
HandsInMotion3tasksgeneral <- HandsInMotion3tasks %>% 
  dplyr::select(id_no, Age_Months, CompositeHandsInMotionTotal,read_fs)

HandsInMotion3tasksgeneral$cAge_Months <- scale(as.numeric(HandsInMotion3tasksgeneral$Age_Months), center = TRUE, scale = FALSE)
```




### **Accuracy**

```{r}
compositeHandsInMotionModel1 <- lm(CompositeHandsInMotionTotal ~ read_fs, data = HandsInMotion3tasksgeneral)
```


```{r}
summary(compositeHandsInMotionModel1)
```






### **Accuracy (+ Age as a co-variate)**

```{r}
compositeHandsInMotionModel2 <- lm(CompositeHandsInMotionTotal ~ cAge_Months + read_fs, data = HandsInMotion3tasksgeneral)
```


```{r}
summary(compositeHandsInMotionModel2)
```







# {-}



# **Background Tests** {.tabset .tabset-pills}

```{r}
HandsInMotionbackgroundWRIT <- read.csv("~/HandsInMotion_WRIT.csv") # ~ INSERT_HOME_DIRECTORY
```



## **WRAT Word Reading Acccuracy** {.tabset .tabset-pills}

### **Descriptive statistics**


#### **Overall**


```{r}
psych::describe(HandsInMotionbackground$WordRAcc_totalScore)
```





## **Word Reading Fluency** {.tabset .tabset-pills}

### **Descriptive statistics**



```{r}
psych::describe(HandsInMotionbackground$WordRF_totalScore_all)
```




## **Pseudoword Reading Fluency** {.tabset .tabset-pills}

### **Descriptive statistics**


```{r}
psych::describe(HandsInMotionbackground$PseudoWordRF_totalScore_all)
```




## **Phoneme Deletion** {.tabset .tabset-pills}

### **Descriptive statistics**



```{r}
psych::describe(HandsInMotionbackground$PD_TotalScore)
```




## **RAN digits and letters** {.tabset .tabset-pills}

### **Descriptive statistics**


```{r}
psych::describe(HandsInMotionbackground$RANcompositeDur)
```




## **Nonverbal IQ** {.tabset .tabset-pills}

### **Descriptive statistics**



```{r}
psych::describe(HandsInMotionbackgroundWRIT$WRIT_stdz)
```



# {-}


# **Correlation Analyses** {.tabset .tabset-pills}


```{r}
HandsInMotion_correlationsFile <- HandsInMotion3tasks %>% 
  dplyr::select(id_no, CompositeHandsInMotionMean, WRATWordR_MeanScore,WordRF_meanScore_all,PseudoWordRF_meanScore_all, RANcompositeDur,PD_TotalScore) %>% 
  mutate(PDmean = PD_TotalScore/40,
         RANcompositeDurMean = RANcompositeDur/4) %>% 
  dplyr::select(-c(PD_TotalScore,RANcompositeDur, id_no))
```



```{r, warning= FALSE}
corr_df <- ggcorrmat(HandsInMotion_correlationsFile, 
          type = "pearson",
          p.adjust.method = "holm",
          cor.vars.names = c("Paired Associate Learning", "Word Reading Accuracy", "Word Reading Fluency", "Pseudoword Reading Fluency", "Phoneme Awareness", "Rapid Automatized Naming"),
          ggtheme = ggplot2::theme_classic(),
          matrix.type = "upper",
          ggcorrplot.args = list(outline.color = "black", hc.order = TRUE),
          colors = NULL, ## turning off manual specification of colors
          palette = "blue_grey_material",
          package = "ggsci", 
          #title = "#####"
          output = "matrix"
)
```


```{r}
corr_df
```



```{r}
corr_df$p.value <- round(corr_df$p.value,3)
```

# {-}


